---
title: "Words and phrases used to search abstracts"
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: 
      toc: false # table of content true
      toc_depth: 1  # 
---
  
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
library(dplyr)
library(tidyr)
library(flextable)

source('99_key_characters_words_phrases.R')
```

A question mark means the preceding character is optional. So 'suggests?' searches for 'suggest' and 'suggests'. Unless specified, the words/phrases are not case sensitive.

## Hedging words/phrases

```{r, results='asis'}
to_show = words_phrases_hedging
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Signposting words/phrases

```{r, results='asis'}
to_show = words_phrases_signposting
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Narrator words/phrases (case sensitive)

```{r, results='asis'}
to_show = words_phrases_narrator
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```


## Negative control

```{r, results='asis'}
to_show = negative_control
to_show = to_show[order(to_show)] # alphabetical
for (word in to_show){
cat('* ', word, '\n')
}
```

# Sex and gender

We used three sets of words to examine sex and gender.

## All words combined

```{r, results='asis'}
to_show = male_words
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

```{r, results='asis'}
to_show = female_words
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Sex words

```{r, results='asis'}
to_show = male_words1
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

```{r, results='asis'}
to_show = female_words1
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Gender words

```{r, results='asis'}
to_show = male_words2
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

```{r, results='asis'}
to_show = female_words2
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

# Hype

We used a range of word sets to investigate hype.

## Importance

```{r, results='asis'}
to_show = hype_words_1
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Novelty

```{r, results='asis'}
to_show = hype_words_2
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Rigor

```{r, results='asis'}
to_show = hype_words_3
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Scale

```{r, results='asis'}
to_show = hype_words_4
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Utility

```{r, results='asis'}
to_show = hype_words_5
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```


## Quality

```{r, results='asis'}
to_show = hype_words_6
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```


## Attitude

```{r, results='asis'}
to_show = hype_words_7
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Problem

```{r, results='asis'}
to_show = hype_words_8
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```

## Additional hype words

```{r, results='asis'}
to_show = hype_words_9
to_show = to_show[order(to_show)]
for (word in to_show){
cat('* ', word, '\n')
}
```


# Misspellings

```{r, results='asis'}
to_show = spelling_words
to_show = to_show[order(to_show)] # alphabetical
for (word in to_show){
cat('* ', word, '\n')
}
```
