---
title: "Plot trends over time for narrator analysis"
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: word_document
---

```{r setup, include=FALSE}
## called by 3_plot_trends.R ###

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
source('99_functions.R')
# libraries
library(dplyr)
library(stringr)
library(flextable)
#library(scales) # for comma
library(ggplot2)
library(gridExtra)
g.theme = theme_bw() + theme(panel.grid.minor = element_blank())
cbPalette = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7",'skyblue','dark red') # added a few more
```

This document contains trend plots for our analysis of language over time in papers published on _PubMed_. In total there were `r format(nrow(abstracts), big.mark=',')` abstracts.

The plots show the mean per year and the 95% confidence interval for the mean (shaded area).

There are two plots per outcome: 

* All articles types combined
* Split by article type

For the results by article type, we excluded years with fewer than 50 abstracts. We did not add confidence intervals to this plot as this made the plot too crowded.

# Signposting

```{r, fig.width=8}
p1 = make_trend_plot(indata = abstracts, outcome = 'signposting')
grid.arrange(p1$combined, p1$strata, ncol=2, widths = c(1, 1.45))
```

# Hedging

```{r, fig.width=8}
p2 = make_trend_plot(indata = abstracts, outcome = 'hedging')
grid.arrange(p2$combined, p2$strata, ncol=2, widths = c(1, 1.45))
```


# Noun chunks

```{r, fig.width=8}
p3 = make_trend_plot(indata = abstracts, outcome = 'noun_chunks')
grid.arrange(p3$combined, p3$strata, ncol=2, widths = c(1, 1.45))
```

# Any narrator 

```{r, fig.width=8}
p4 = make_trend_plot(indata = abstracts, outcome = 'narrator')
grid.arrange(p4$combined, p4$strata, ncol=2, widths = c(1, 1.45))
```

This is a binary yes or no outcome, whereas the other outcomes are counts.

# Misspellings 

```{r, fig.width=8}
p5 = make_trend_plot(indata = abstracts, outcome = 'spelling')
grid.arrange(p5$combined, p5$strata, ncol=2, widths = c(1, 1.45))
if(export==TRUE){
  jpeg('figures/misspellings.jpg', width=5, height=4, units='in', res=600, quality=100)
  print(p5$combined)
  invisible(dev.off())
}
```

# Negative control

```{r, fig.width=8}
p7 = make_trend_plot(indata = abstracts, outcome = 'control', label = 'Negative control')
grid.arrange(p7$combined, p7$strata, ncol=2, widths = c(1, 1.45))
```

# Verbs  

```{r, fig.width=8}
p8 = make_trend_plot(indata = abstracts, outcome = 'VERB', label = 'Verbs')
grid.arrange(p8$combined, p8$strata, ncol=2, widths = c(1, 1.45))
```

# Nouns

```{r, fig.width=8}
p9 = make_trend_plot(indata = abstracts, outcome = 'NOUN', label = 'Nouns')
grid.arrange(p9$combined, p9$strata, ncol=2, widths = c(1, 1.45))
```

# Numbers

```{r, fig.width=8}
# see https://universaldependencies.org/u/pos/NUM.html
p10 = make_trend_plot(indata = abstracts, outcome = 'NUM', label = 'Numbers')
grid.arrange(p10$combined, p10$strata, ncol=2, widths = c(1, 1.45))
```

Labelled "numbers", but includes numerals such as "11:00" or "one".

# Number of words per sentence

```{r, fig.width=8}
exclude_handful = filter(abstracts, words_per_sentence < 400) # exclude a few errors
p11 = make_trend_plot(indata = exclude_handful, outcome = 'words_per_sentence', label = 'Words per sentence')
grid.arrange(p11$combined, p11$strata, ncol=2, widths = c(1, 1.45))
```


# Summary plot

```{r, fig.width=9, fig.height=9}
# add titles
p1$combined = p1$combined + ggtitle('Signposting')
p2$combined = p2$combined + ggtitle('Hedging')
p3$combined = p3$combined + ggtitle('Noun chunks')
p4$combined = p4$combined + ggtitle('Any narrator')
p5$combined = p5$combined + ggtitle('Misspelling')
p7$combined = p7$combined + ggtitle('Negative control')
p8$combined = p8$combined + ggtitle('Verbs')
p9$combined = p9$combined + ggtitle('Nouns')
p10$combined = p10$combined + ggtitle('Numbers')
# plot
grid.arrange(p1$combined, p2$combined, p3$combined, 
             p4$combined, p5$combined, p7$combined, 
             p8$combined, p9$combined, p10$combined, nrow=3)
```

# Male and Female

Here we look at the results for male and female words.

### All male and female words

```{r, fig.width=8}
p6 = make_trend_plot(indata = abstracts, outcome = c('male','female'), legend_position = legend_position) 
grid.arrange(p6$combined, p6$strata, ncol=2, widths = c(1, 1.45))
```

### Sex: Male and female

Includes male, males, female and females.

```{r, fig.width=8}
legend_position[1] =  legend_position[1] - 0.05 # needs to go further left
p6a = make_trend_plot(indata = abstracts, outcome = c('male1','female1'), category_labels = c('Male sex','Female sex'), legend_position = legend_position) 
grid.arrange(p6a$combined, p6a$strata, ncol=2, widths = c(1, 1.45))
```

### Gender: Man and woman

Uses man, men, boy, women, woman, girl and all plurals.

```{r, fig.width=8}
p6b = make_trend_plot(indata = abstracts, outcome = c('male2','female2'), category_labels = c('Male gender','Female gender'), legend_position = legend_position) 
grid.arrange(p6b$combined, p6b$strata, ncol=2, widths = c(1, 1.45))
```


# Hype

Here we examine our definitions of hype.

## Importance

```{r, fig.width=8}
h1 = make_trend_plot(indata = abstracts, outcome = 'hype1', label = 'Importance')
grid.arrange(h1$combined, h1$strata, ncol=2, widths = c(1, 1.45))
```

## Novelty

```{r, fig.width=8}
h2 = make_trend_plot(indata = abstracts, outcome = 'hype2', label = 'Novelty')
grid.arrange(h2$combined, h2$strata, ncol=2, widths = c(1, 1.45))
```

## Rigor

```{r, fig.width=8}
h3 = make_trend_plot(indata = abstracts, outcome = 'hype3', label = 'Rigor')
grid.arrange(h3$combined, h3$strata, ncol=2, widths = c(1, 1.45))
```

## Scale

```{r, fig.width=8}
h4 = make_trend_plot(indata = abstracts, outcome = 'hype4', label = 'Scale')
grid.arrange(h4$combined, h4$strata, ncol=2, widths = c(1, 1.45))
```

## Utility

```{r, fig.width=8}
h5 = make_trend_plot(indata = abstracts, outcome = 'hype5', label = 'Utility')
grid.arrange(h5$combined, h5$strata, ncol=2, widths = c(1, 1.45))
```

## Quality

```{r, fig.width=8}
h6 = make_trend_plot(indata = abstracts, outcome = 'hype6', label = 'Quality')
grid.arrange(h6$combined, h6$strata, ncol=2, widths = c(1, 1.45))
```

## Attitude

```{r, fig.width=8}
h7 = make_trend_plot(indata = abstracts, outcome = 'hype7', label = 'Attitude')
grid.arrange(h7$combined, h7$strata, ncol=2, widths = c(1, 1.45))
```

## Problem

```{r, fig.width=8}
h8 = make_trend_plot(indata = abstracts, outcome = 'hype8', label = 'Problem')
grid.arrange(h8$combined, h8$strata, ncol=2, widths = c(1, 1.45))
```

## Additional hype words

```{r, fig.width=8}
h9 = make_trend_plot(indata = abstracts, outcome = 'hype9', label = 'Hype')
grid.arrange(h9$combined, h9$strata, ncol=2, widths = c(1, 1.45))
```

## Summary plot for hype

```{r}
to_plot = mutate(abstracts, year = as.numeric(format(date, '%Y'))) %>%
  select(year, n.words, starts_with('hype')) %>%
  pivot_longer(cols=starts_with('hype'), names_to = "type", values_to = "outcome") %>%
  mutate(dependent = 100*(outcome / n.words)) %>%
  group_by(year, type) %>%
  summarise(mean = mean(dependent)) %>%
  ungroup()
# 
hlabels = c('Importance','Novelty','Rigor','Scale','Utility','Quality','Attitude','Problem','Additional')
splot = ggplot(data=to_plot, aes(x=year, y=mean, col=type))+
  geom_line(size=1.04)+
  scale_color_manual(NULL, values=cbPalette, labels = hlabels)+
  xlab('Year')+
  ylab('Per 100 words')+
  theme_bw()+
  theme(panel.grid.minor = element_blank(),
        legend.position = 'right')
splot
```

