---
title: "Plot trends over time for narrator analysis. Version stratified by country of affiliation."
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: word_document
---

```{r setup, include=FALSE}
## called by 3_plot_trends.R ###

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
source('99_functions.R')
# libraries
library(dplyr)
library(stringr)
library(flextable)
#library(scales) # for comma
library(ggplot2)
library(gridExtra)
g.theme = theme_bw() + theme(panel.grid.minor = element_blank())
# colour schemes:
colours = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7",'skyblue','dark red') # added a few more
colours = as.character(yarrr::piratepal('basel'))

## Find the top ten countries
top.ten = group_by(abstracts, country) %>%
  tally() %>%
  arrange(-n) %>%
  slice(1:10) %>%
  pull(country)
abstracts = filter(abstracts, country %in% top.ten) %>%
  mutate(country = ifelse(is.na(country), 'missing', country))
```

This document contains trend plots for our analysis of language over time in papers published on _PubMed_. In this analysis we look at trends over time by the top ten countries. In total there were `r format(nrow(abstracts), big.mark=',')` abstracts after restricting to the top ten countries.

The plots show the mean per year. We do not show the 95% confidence interval for the mean, because the plot would be too busy.

We exclude the yearly results for a country if there were fewer than 50 abstracts that year. 

# Signposting

```{r, fig.width=8}
p1 = make_trend_plot_country(indata = abstracts, outcome = 'signposting')
print(p1)
```

# Hedging

```{r, fig.width=8}
p2 = make_trend_plot_country(indata = abstracts, outcome = 'hedging')
print(p2)
```


# Noun chunks

```{r, fig.width=8}
p3 = make_trend_plot_country(indata = abstracts, outcome = 'noun_chunks')
print(p3)
```

# Any narrator 

```{r, fig.width=8}
p4 = make_trend_plot_country(indata = abstracts, outcome = 'narrator')
print(p4)
```

This is a binary yes or no outcome, whereas the other outcomes are counts.

# Misspellings 

```{r, fig.width=8}
p5 = make_trend_plot_country(indata = abstracts, outcome = 'spelling')
print(p5)
if(export==TRUE){
  jpeg('figures/misspellings_country.jpg', width=5, height=4, units='in', res=600, quality=100)
  print(p5)
  invisible(dev.off())
}
```

# Negative control

```{r, fig.width=8}
p7 = make_trend_plot_country(indata = abstracts, outcome = 'control', label = 'Negative control')
print(p7)
```

# Verbs  

```{r, fig.width=8}
p8 = make_trend_plot_country(indata = abstracts, outcome = 'VERB', label = 'Verbs')
print(p8)
```

# Nouns

```{r, fig.width=8}
p9 = make_trend_plot_country(indata = abstracts, outcome = 'NOUN', label = 'Nouns')
print(p9)
```

# Numbers

```{r, fig.width=8}
# see https://universaldependencies.org/u/pos/NUM.html
p10 = make_trend_plot_country(indata = abstracts, outcome = 'NUM', label = 'Numbers')
print(p10)
```

Labelled "numbers", but includes numerals such as "11:00" or "one".

# Number of words per sentence

```{r, fig.width=8}
exclude_handful = filter(abstracts, words_per_sentence < 400) # exclude a few errors
p11 = make_trend_plot_country(indata = exclude_handful, outcome = 'words_per_sentence', label = 'Words per sentence')
print(p11)
```

# Summary plot

```{r, fig.width=9, fig.height=9}
# add titles
p1 = p1 + ggtitle('Signposting') + theme(legend.position = 'none')
p2 = p2 + ggtitle('Hedging') + theme(legend.position = 'none')
p3 = p3 + ggtitle('Noun chunks') + theme(legend.position = 'none')
p4 = p4 + ggtitle('Any narrator') + theme(legend.position = 'none')
p5 = p5 + ggtitle('Misspelling') + theme(legend.position = 'none')
p7 = p7 + ggtitle('Negative control') + theme(legend.position = 'none')
p8 = p8 + ggtitle('Verbs') + theme(legend.position = 'none')
p9 = p9 + ggtitle('Nouns') + theme(legend.position = 'none')
p10 = p10 + ggtitle('Numbers') + theme(legend.position = 'none')
# plot
grid.arrange(p1, p2, p3, 
             p4, p5, p7,  # p6 is in gender below
             p8, p9, p10, nrow=3)
```

# Male and Female

Here we look at the results for male and female words.

### All male words

```{r, fig.width=8}
p6m = make_trend_plot_country(indata = abstracts, outcome = 'male')
p6m
```

### All female words

```{r, fig.width=8}
p6f = make_trend_plot_country(indata = abstracts, outcome = 'female')
p6f
```

### Sex: Male


```{r, fig.width=8}
sm = make_trend_plot_country(indata = abstracts, outcome = 'male1')
sm
```

### Sex: Female


```{r, fig.width=8}
sf = make_trend_plot_country(indata = abstracts, outcome = 'female1')
sf
```

### Gender: Male


```{r, fig.width=8}
gm = make_trend_plot_country(indata = abstracts, outcome = 'male2')
gm
```

### Gender: Female


```{r, fig.width=8}
gf = make_trend_plot_country(indata = abstracts, outcome = 'female2')
gf
```

# Hype

Here we examine our definitions of hype.

## Importance

```{r, fig.width=8}
h1 = make_trend_plot_country(indata = abstracts, outcome = 'hype1', label = 'Importance')
print(h1)
```

## Novelty

```{r, fig.width=8}
h2 = make_trend_plot_country(indata = abstracts, outcome = 'hype2', label = 'Novelty')
print(h2)
```

## Rigor

```{r, fig.width=8}
h3 = make_trend_plot_country(indata = abstracts, outcome = 'hype3', label = 'Rigor')
print(h3)
```

## Scale

```{r, fig.width=8}
h4 = make_trend_plot_country(indata = abstracts, outcome = 'hype4', label = 'Scale')
print(h4)
```

## Utility

```{r, fig.width=8}
h5 = make_trend_plot_country(indata = abstracts, outcome = 'hype5', label = 'Utility')
print(h5)
```

## Quality

```{r, fig.width=8}
h6 = make_trend_plot_country(indata = abstracts, outcome = 'hype6', label = 'Quality')
print(h6)
```

## Attitude

```{r, fig.width=8}
h7 = make_trend_plot_country(indata = abstracts, outcome = 'hype7', label = 'Attitude')
print(h7)
```

## Problem

```{r, fig.width=8}
h8 = make_trend_plot_country(indata = abstracts, outcome = 'hype8', label = 'Problem')
print(h8)
```

## Additional hype words

```{r, fig.width=8}
h9 = make_trend_plot_country(indata = abstracts, outcome = 'hype9', label = 'Hype')
print(h9)
```


